---
title: Evolution or revolution
author: Benjamin Gravesteijn
date: '2019-05-24'
slug: evolution-or-revolution
categories: ["Conference"]
tags: ["Publications", "Education", "Rewarding"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r, echo=FALSE}
blogdown::shortcode('tweet', '1130465707664334849')
```


Yesterday, I attended a meeting organized by the main Dutch funding organizations [ZonMW](<https://www.zonmw.nl/nl/>) and the [NWO](<https://www.nwo.nl/>), called ["Evolution or Revolution"](https://www.zonmw.nl/nl/actueel/agenda/detail/item/evolutie-of-revolutie/), together with Daphne Voormolen. The aim of the meeting was to have an open discussion. One where we, as researchers, were asked what they, as funders, could do to help create financial incentives to improve the scientific community. Through panel discussions, break-out sessions, and interactive [menti-questions](https://menti.com), we discussed how the scientific community in 2030 will have to function. The quintessential question was how the field would transform, through evolution, or revolution.

## Cultural changes
"We are competing and focusing on only such a small fraction of academic work" was commented by someone from the audience at the end of the day. This comment resonates still with me today. A lot of people agreed that competition was necessary in academia, and that competition improves the quality of the work. However, everybody agreed that the cultural systems that are in place rigth now to facilitate competition, are failing.

One of the symptoms of the failing competitive system is the stigma that exists around stepping up and stepping down in academia. [Rianne Letschert](https://twitter.com/Rianneletschert) explained how she was looked down upon when she accepted the honourable position as rector magnificus at Maastricht University. "She must have failed in her academic career", was the comments that she received. While in reality, she took the job just after she received a Veni grant: one of the more prestigious research grants of the [NWO](<https://www.nwo.nl/>). She was able to offer two of her employees a permanent position, so her academic career was -in current terms- definitely succesful. She decided to accept the position as rector maginificus, because she felt that she was needed over there. Both Rianne Letschert as well as [Jet Bussemakers](https://twitter.com/jet_bussemaker) (former minister of science, now professor at the LUMC) proved that our current way of thinking about academic careers is flawed: instead of the 4-tiered ladder (PhD-Postdoc-Associate professor-Professor), a more dynamic, diverse, and personalized career flow should be made possible. 

One of the ways a more dynamic career flow would improve academia is through education. After all, it is one of the three pillars of academia are _creation of knowledge (research)_, _distribution of knowledge (education)_, and _creating impact_ in society. Currently, in terms of rewarding academic work, education is undervalued compared to research. [Jeroen Geurts](https://www.narcis.nl/person/RecordID/PRS1254216/Language/nl), professor a the VU Amsterdam and chairman of ZonMW, explained that he let his employees at the VU decide whether they wanted to focus on education, or on research. This meant that they were recognized by their efforts in their respective profiles. Geurts stated that "strangely enough, the people who had an education profile improved their skills in research, while people with a research profile improved their educational skills." Because the pressure to excell in all fields was no longer present, people could focus on their main abilities. This strengthened their confidence, and let to "collateral improvement". This story inspired me, as well as the audience, and lead to the question how to increase this through financial incentives.  

## Financial incentives
Since the meeting was organized by funders, the means to improve academia that was discussed most often was funding. There were discussions on how through improved funding systems, both diversity, team science, and education could be recognized and appreciated. 

```{r, echo=FALSE}
blogdown::shortcode('tweet', '1131482016715890688')
```

Currently, "excellency" is one of the requirements for a grant proposal to be accepted. However, Anne de Vries, the chairwoman of the national [PhD-network](https://www.hetpnn.nl/2011/04/12/bestuur-3/), could not think of another competence as irrelevant as the competence "excellence": "One can excell at educating, formulating research questions, bringing people together et cetera. But nobody knows how to define general excellency". To measure excellency was one of the most debated issues of the day, and at the end no real criteria could be formulated. One of the most interesting ideas I've heard was to add space in grant proposals where researchers could limitlessly express why they are excellent. This could disencourage strategic behaviour, and potentially foster diversity.

There was general consensus on the fact that the current funding system does not sufficiently recognize team science. After all: "even Einstein did not walk alone". This led to the idea that the system of "principal investigators" generally does not reflect the team that leads big projects. It should be said that the term still applies for specific, mostly local, projects where one researcher actually is the one responsible for the project. However, big projects where multiple centers or countries are collaborating are in practice led by a team, while often the principal investigator receives the actual credits. It is not remarkible that this should change.

Finally, in our own break-out session we discussed how education could find its way in the grant proposal. This could result in stimulating education, through funding. This discussion was complex, and multiple ideas were proposed but did not stick. My favourite idea (although still very abstract) was that research and education is often much more intertwined than we believe it is. Therefore, education can be seen as one of the results, or realizations, of research. Finally, we did discuss current funding for education, which in the Netherlands is organized by [the Comenius network](https://www.knaw.nl/nl/de-knaw/comeniusnetwerk). We agreed that general awareness of these funding systems is scarce and that this should be promoted.

## The PhD system
"The PhD system is the source of all evil" was the statements that one of the break-out sessions came up with. Although everybody agreed that this was put too strongly, this statement did spart out the most interactive discussion of the day. A PhD-education is at the doorway to an academic career. By shaping this part of the career, we could improve the future academic culture.

The main thing that I will remember from the discussion is that the phd system is flawed because it evaluates only one aspect of academic work. Since it is the training program for academics, it should evaluate all three pillars of academic work. Currently, only research output is recognized. Moving forward, we should redefine criteria for getting a PhD, taking into account what was achieved on educational and translational aspects of science.

##Conclusion
At the end of the day, Daphne and I sat down with a beer and were both amazed by the honesty of the discussions. This probably was the result of a top-down organized meeting by the funders. The goal of the day was not to convince the current institutions how we want our field to move forward. On the contrary, the institutions asked us how we would like to be evaluated and recognized. This, for me, was the most inspirational of the day and made me feel honoured to be a researcher in the Netherlands. We have a lot to improve, but at least we try.