---
title: TBI, beer, and chocolates in Leuven
author: Benjamin Gravesteijn
date: '2019-09-12'
slug: tbi-beer-and-chocolates-in-leuven
categories:
  - Conference
tags:
  - Publications
  - Anesthesia
  - Leuven
---

```{r, echo=FALSE}
blogdown::shortcode('tweet', '1170664414007181313')
```

For the last month, I have been staying in Cambridge, as you perhaps have read before. However, last week was a little different. I have been flying quite a lot this year: Japan, Vienna, Cambridge, Milan... But my final trip of 2019 commenced last week: a conference in the former beer capitol of the world, Leuven.

## Home
One of the best things about Leuven, is that the city is only a 2 hour journey away from home. It didn't come as a surprise that after more than a month from home, I would miss the people at home. Therefore, I couldn't be more happier to be able to see Tom and my mother, never mind how short. They stayed over for the weekend before the conference started. Although it was too short to cure homesickness completely, I'm sure that the boost of joy this weekend weekend will get me through the remainder of my stay.

Another boost came of course from the city itself. As someone with an appetite for beer, the former beer capitol of the world felt like Disney land. But before you take me as an alcoholic, please be aware that walking around in a city drowned in beer culture, felt just as energizing as the nightlife. Additionally, one in every three inhabitants of Leuven is a student, or is associated with the university. Finally, as I was also able to speak Dutch again, it really felt a little bit as home.

## ICP2019
The conference itself was held in the medical campus of the KU Leuven. Walking up the campus (it was situated on a hill), I was amazed by the size of it all. It didn't come as a surprise to hear that it apparently is the biggest hospital of Europe. However, I'm a bit sceptical about that...

The conference itself was a very interesting, productive, and fun one. It was a conference with a lot of interaction between speakers and audience. The keynote speakers were all of great quality, with whom the audience was not to anxious to confront in discussions. An example was when Nino Stochetti talked about a novel technique to measure oxygen saturation in the brain: NIRS. Nino was quite sceptical about the technique: he showed a study which showed that the oxygen saturation in the brain measured by NIRS between alive and brain-dead people doesn't differ that much... However, the room was full of people who enthusiastically use NIRS (for both research and clinical practice). Therefore the discussion that followed was intense and interesting. But luckily, Nino managed to dissolve the discussion with a nice adequate joke, to release the tension in the room. There will be more discussions about this technique on next conferences...

```{r, echo=FALSE}
blogdown::shortcode('tweet', '1171407807121416193')
```

Of course, I should not forget to mention my first ever oral presentation at the conference. I was quite scared when I saw the room: as big as both our lecture halls combined! But I was lucky to be in the session after Nino, [which is a collaborator on the study that I presented](https://bgravesteijn.netlify.com/2019/07/09/writer-s-visit-to-milan/). Discussing it with him on beforehand released some of the tension. The presentation itself went great, especially after learning that nobody heard my dry mouth during the last couple of minutes. After the talk, I got back that this study "reflects what we see in real practice", and that "it was balanced enough to convince me". Now, the next step of course is to obtain all feedback from the co-authors and publish it: one step closer to my PhD!

## Back in Cambridge
And now, back in Cambridge, the first days of work have been full of motivation and energy. This trip was apparently exactly what I needed to make the remainder of my stay as succesfull as possible. At least I now know that I can return saying that I learned and experienced as much as I could. But most importantly, I feel as proud as I can.